---
title: "Simple document"
author: Danchen
date: 2025-09-11
output: 
  github_document:

---

I'm an R Markdown document! 

```{r}
library(tidyverse)
```




# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r collapse=TRUE}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

This is where I'm going to talk about code chunks.

```{r}
mean(samp)
sd(samp)
```

Let's also make a dataframe.

```{r}
example_df <- 
  tibble(
    vec_numeric = 1:4,
    vec_char = c("My", "name", "is", "jeff"),
    vec_factor = factor(c("male", "male", "female", "female"))
  )
```

Let's make a plot an d see how cool that is!

```{r}
plot_df = 
  tibble(
    x = rnorm(1000, mean = 1, sd = .5),
    y = 1 + 2 * x + rnorm(1000)
  )

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

This is a neat scatterplot!!

This chunk does one of the learning assessment.

```{r}
la_df <- 
  tibble(
    numeric_samp = rnorm(500, mean = 1),
    greater_0 = numeric_samp > 0,
    abs_val_samp = abs(numeric_samp)
  )

ggplot(la_df, aes(x = abs_val_samp)) + geom_histogram()
```

To use inline code, I would do sth like: "The sample size in the new 
dataframe is `r nrow(la_df)` "

Something more complex is "The mean of my new variable is `r mean(pull(la_df, abs_val_samp))`."


# Let's look at formatting

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell








